COG-ED Manuscript

### 2021-12-16 06_Paper/COG-ED/Manuscript.Rmd

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package

@@

  # get subset for MLM

  h2b_sub <- droplevels(subset(h2b_data[c("subject", "level", "sv", "d", "correct", "postcorrect", "rt", "nfc")],
                               subset = !is.na(rt)))

@@

The multilevel model `r replication_table`

statistically significant effect of n-back load level `r apa_print(m1_h2b)$full_result$level_cwc`
controlled for performance and correct and post-correct answers

`r apa_print(m1_h2b)$full_result$nfc_cgm`
`r round((icc_h2b*100), digits = 0)` % of the total variance in subjective values can be explained by differences between subjects ($ICC =$ `r round(icc_h2b, digits = 2)`).

simple slopes analysis `r h2b_ssa.table`, `r h2b_jnplot`,`r h2b_ssa.plot`
statistically significant influence of n-back load level on subjective value, but no moderating effect of NFC

>>>>

  knitr::opts_chunk$set(echo = TRUE)
  library(bibtex)
  library(here)         # to set a directory without defined paths, "here" package
  library(tidyverse)    # plotting and managing data, "tidyverse" package
  library(bayestestR)   # computing area under the curve, "bayestestR" package
  library(papaja)       # APA conform output, "papaja" package
  library(lmerTest)     # for multilevel modeling
  library(afex)         # compute repeated measures ANOVA, "afex" package
  library(emmeans)      # for custom contrasts in ANOVAs, "emmeans" package
  library(sjPlot)       # plot MLM model fit
  library(kableExtra)   # 
  library(interactions) # for simple slopes analysis
  library(huxtable)     # create huxtable

@@

  # get subset for MLM without RT = NA

  h2b_data <- droplevels(subset(h2b_data[c("subject", "level", "sv", "dprime", "correct", "postcorrect", "rt", "nfc")],
                               subset = !is.na(rt)))

@@

N-back level is a reliable predictor of subjective value (`r apa_print(m1_h2b)$full_result$level_cwc`), even after controlling for declining task performance (signal detection d’ and reaction time) as well as correct and post-correct answers. 
The results of the multilevel model are detailed in Table X. 
`r replication_table`
`r round((icc_h2b*100), digits = 0)` % of the total variance in subjective values can be explained by differences between subjects ($ICC =$ `r round(icc_h2b, digits = 2)`).
However, NFC has no statistically significant effect on subjective value (`r apa_print(m1_h2b)$full_result$nfc_cgm`).
The simple slopes analysis revealed a significant slope of n-back level for three different expressions of NFC (Table X, Figure X).
`r h2b_ss.table`
`r h2b_ss.plot`
The Johnson-Neyman plot (Figure x) visualizes the significance of the slope of n-back level at different values of NFC. The Johnson-Neyman interval is [`r h2b_jn.int`]. Consequently, the slope of n-back level is not significant for individuals with very low NFC values.    
`r h2b_jn.plot`

## alternative: `r h2b_jn`
